%doc stuff
\documentclass[a4paper,11pt]{article}
\usepackage[portuguese, english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[top=1cm, bottom=1cm, left=2.5cm, right=2.5cm]{geometry}
%\usepackage{palatino}
%kyperlinks
\usepackage[colorlinks=true, urlcolor=blue]{hyperref}
\usepackage{url} 
%tables
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{multicol}
\usepackage{makecell}
\usepackage{float}
\usepackage[singlelinecheck=false]{caption} % para tirar o tituli à tabela
\usepackage{enumitem}
\setlist{itemsep=4pt}

\begin{document}
\thispagestyle{empty} 
\renewcommand\arraystretch{1.1}
\begin{center}
\begin{tabularx}{\linewidth}{XX}
\multicolumn{2}{c}{\textbf{\Large{Bárbara Abreu}}} \\
\midrule[1pt]
\midrule[0.5pt]
\multicolumn{2}{c}{\textit{\footnotesize{Full Name: \textbf{Bárbara} Palma de \textbf{Abreu} Caldeira Pinto } }}\\
\makecell[c]{\href{https://www.linkedin.com/in/barbarabreu-43183a28/}{Linkedin}} & \makecell[c]{\href{https://github.com/barbara-abreu/}{Github}} \\
\makecell[c]{Mail: brbr\_abreu@yahoo.com}  & \makecell[c]{Telephone: +351932822880} \\
\makecell[c]{Nationality: Portuguese} & \makecell[c]{Date of birth: 08-08-1991} \\
\end{tabularx}




\begin{tabularx}{\linewidth}{X}
\renewcommand\arraystretch{1.5}
\makecell[c]{\textbf{Profile$\colon$}} \\
\makecell[c] {A PhD graduate passionate for models, with broad IT and data analysis knowledge,\\ seeks an exciting opportunity as a quantitative modeller{\slash}data scientist.}
\newline \\
\bottomrule[1pt]
\end{tabularx}

\begin{tabularx}{\linewidth}{X}
\textbf{IT skills$\colon$}
\begin{itemize}
\item Proficient in the Linux operative system, in Ubuntu and Fedora distributions. 
\item Experienced in Bash, AWK and Python programming. Also knowlegeable of commonly used libraries in Python: Numpy, Pandas , Sklearn, Statsmodels. 
\item Knowledge of SQL, and of the usage of PostgreSQL and MSSQL.
%\item Knowledge of Docker container system, GitLab platform and Kubernetes.
\item Knowledge of the document preparation system \LaTeX.
\item Proficient in the Windows operative system, Microsoft Word, Excel, PowerPoint and Adobe Photoshop.
\item  Experienced in scientific software: GROMACS, PLUMED plugin,AutoDock, Vina, MEAD, PETIT, Pymol, ChemDraw, MarvinSketch, MDAnalysis.
\end{itemize}
\end{tabularx}

\begin{tabularx}{\linewidth}{X}
\textbf{Problem solving-skills$\colon$}
\begin{itemize}
\item Implemented various protocols  for simulation preparation, result analysis and processing, using Python, AWK and bash scripting. Such an example is the creation of the protocols and pipelines for umbrella sampling simulation, namely the preparation, processing and result analysis.
\end{itemize} 
\end{tabularx}


\begin{tabularx}{\linewidth}{X}
\textbf{People and project management skills$\colon$}
\begin{itemize}
\item Often involved in undergraduate students supervision, during short internships (one week), such as Summer Science 2019, in which I conceived and supervised a small project.
\item Involved in the creation of the Portuguese Young Biophysicists association and on the organization of the first “Biophysics Party” at 6\textsuperscript{th} July 2018.
\item Involved in the organization of the fourth encounter of young researchers in structural computational biology \textit{``Encontro de Jovens Investigadores de Biologia Computacional Estrutural``} 2016.
\end{itemize}
\end{tabularx}

\begin{tabularx}{\linewidth}{X}
\textbf{Communication skills$\colon$}
\begin{itemize}
\item Participation in international and national scientific conferences for communicating my research.
\item Participation in science communication and outreach activities, such as ITQB’s open days and the reception to the 2018 International Physics Olympiads.
\end{itemize}
\end{tabularx}



\begin{tabularx}{\linewidth}{X}
\textbf{Language skills$\colon$}
\begin{itemize}
\item Mother tongue: Portuguese
\item Other languages: English – Fluent (C1 level according to the Common European Framework of Reference for Languages: Learning, Teaching, Assessment (CEFR))
\end{itemize} \\
%\bottomrule[1pt]
\end{tabularx}


\begin{tabularx}{\linewidth}{XX}
\toprule[1pt]
\textbf{Education$\colon$}
\begin{itemize}
\item \emph{2020} \textit{\textbf{PhD in Biophysics}}   ITQB-NOVA, Oeiras, Portugal 
\newline
Expected date of completion: October 2020 \newline
Thesis title$\colon$ \emph{``The structural basis of substrate translocation in ABC transporters: a biomolecular simulation approach``.} 
My work  the function of ABC transporters using computational methodologies, such as molecular modelling and simulation.
\item \emph{2014} \textit{\textbf{Master in Medicinal Chemistry}} University of Minho, Braga, Portugal
\newline
Modules carried included medicinal chemistry, medicinal inorganic chemistry, molecular modelling and organic chemistry.
\item \emph{2012}  \textit{\textbf{Degree in Biochemistry}}  University of Minho, Braga, Portugal
\newline
My degree in biochemistry included modules of math (linear algebra, calculus and statistics), chemistry, physics, biology and biochemistry.
\end{itemize} \\
\bottomrule[1pt]
\thispagestyle{empty} 
\end{tabularx}

\begin{tabularx}{\linewidth}{XX}
\textbf{Complementary training$\colon$}
\begin{itemize}
\item \emph{2020} ``\emph{\textbf{Scientific Text Processing with}} \LaTeX`` NOVA Doctoral School - Universidade Nova de Lisboa
\item \emph{2020} ``\emph{\textbf{Python for Finance: Investment Fundamentals \& Data Analytics}} Udemy Certificate UC-14ce25c0-98e0-42e0-b2b6-20a7e625c3ee earned on Monday, 06 June 2020
\item \emph{2020} ``\emph{\textbf {SQL \& Database Design A-Z\textsuperscript{TM}$\colon$ Learn MS SQL Server $+$ PostgreSQL}}`` Udemy. Certificate UC-2475ef40-a81e-46b3-a5f8-49ab1229b481 earned on Wednesday, 06 May 2020
\item \emph{2020} ``\emph{\textbf{Finance for the Real World - Corporate Finance 101}} Certificate UC-3aad7239-3cb9-4c04-b095-bb146cb68369 earned on Saturday, May 16, 2020
\item \emph{2020} ``\emph{\textbf {Python for Data Science and Machine Learning Bootcamp}}`` Udemy. Certificate UC-b9ee0789-b45e-414d-8f53-7e0e8d512671 earned on Saturday, March 28, 2020
\item \emph{2020} ``\emph{\textbf {ResOps: Cloud-native tools and technology for researchers}}`` EMBL-EBI online course
\item \emph{2019} ``\emph{\textbf {Statistics for Economics and Management}}`` in the Economics Bachelor at NOVA School of Business and Economics, Portugal.
\item \emph{2018} ``\emph{\textbf {Machine Learning by Stanford University}}`` on Coursera. Certificate 5AK7S9BS8H5D earned at Friday, July 13, 2018 9$\colon$34 PM GMT
\item \emph{2017} ``\emph{\textbf {Project Management Course}}``  NOVA Doctoral School - Universidade Nova de Lisboa
\item \emph{2016} ``\emph{\textbf {Data processing automation in Python}}``  NOVA Doctoral School - Universidade Nova de Lisboa
\item \emph{2015} ``\emph{\textbf {Research Skills Development Course}}`` NOVA Doctoral School – Universidade Nova de Lisboa
\item \emph{2013} ``\emph{\textbf {English Language Course – Level C1}}`` BabeliUM – University of Minho
\end{itemize} \\
\bottomrule[1pt]
\end{tabularx}

\begin{tabularx}{\linewidth}{X}
\textbf{Other work experience$\colon$}
\begin{itemize}
\item \textit{2014} \textbf{Collaborator at Caldeira Pinto Unipessoal Lda.} - Involved in the manufacturing of household goods.
\end{itemize}
\end{tabularx}

\end{center}
\thispagestyle{empty} 
\end{document}

